The {TestIdeals} package for \emph{Macaulay2}

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Addressed Pedro's comments.

\subsection{Parameter test modules}
%
\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
%
Given an $F$-finite reduced ring $R$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.  As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.

\begin{definition}
   The \emph{parameter test submodule} is the smallest submodule $M \subseteq \omega_R$ (and hence ideal of $R$, since $M \subseteq \omega_R \subseteq R$) that agrees generically with $\omega_R$ and that satisfies
   %
   \pedro{What is the quantifier for $e$ here?}
   %
\[
T (M^{1/p^e}) \subseteq M.
\]
\end{definition}

@@

If such a $\Phi_e$ exists, it can be identified to a generator of the module $(I^{[p^e]} : I) / I^{[p^e]}$ by Fedder's Lemma \cite{FedderFPureRat}.  Hence we can find a corresponding\footnote{This is done via the function \texttt{QGorensteinGenerator}. } $u \in I^{[p^e]} : I$.  In this case, if $c \in S$ is the pre-image of a test element of $R$, then setting $I_0 = cR$, it follows that
\[
\tau(R) = {\tt ascendIdeal(e, u, I_0)},
\]
where \texttt{ascendIdeal} is the method explained above, in \autoref{eq.AscendIdealExplanation}.
The $e$ here means all Frobenius roots are taken as multiples of $e$.
%
\pedro{I am not sure what this last sentence is saying}
%

@@

Recall that  $\Hom_R( R^{1/p^e}, R)$  is a principal $R^{1/p^e}$-module generated
the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
If $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$, with $1\in B$, then 
$R^{1/p^e}$ is a free $R$-module with basis
$$\left\{ b\,  x_1^{\alpha_1/p^e} \cdots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e, b\in B \right\} ;$$
the trace map $T$ is the projection onto the free summand
$R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.
%
\pedro{This paragraph is a bit redundant; we could just refer to Section~\ref{ss: math behind}}
%

>>>>

\subsection{Parameter test modules}
%
%\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
%
Given an reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.  As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.

\begin{definition}
   The \emph{parameter test submodule} is the smallest submodule $M \subseteq \omega_R$ (and hence ideal of $R$, since $M \subseteq \omega_R \subseteq R$) that agrees generically with $\omega_R$ and that satisfies
   %
   %\pedro{What is the quantifier for $e$ here?}
   %
\[
T (M^{1/p^e}) \subseteq M
\]
for some $e > 0$ (or equivalently for all $e > 0$).
\end{definition}

@@

If such a $\Phi_e$ exists, it can be identified to a generator of the module $(I^{[p^e]} : I) / I^{[p^e]}$ by Fedder's Lemma \cite{FedderFPureRat}.  Hence we can find a corresponding\footnote{This is done via the function \texttt{QGorensteinGenerator}. } $u \in I^{[p^e]} : I$.  In this case, if $c \in S$ is the pre-image of a test element of $R$, then setting $I_0 = cR$, it follows that
\[
\tau(R) = {\tt ascendIdeal(e, u, I_0)},
\]
where \texttt{ascendIdeal} is the method explained above, in \autoref{eq.AscendIdealExplanation}.
The $e$ here means all Frobenius roots are taken as multiples of $e$.  In other words, we first compute ${\tt I_0 +  (u \cdot I_0)^{1/p^{[e]}}}$.  Then we compute 
\[
{\tt I_0 +  (u\cdot I_0)^{1/p^{[e]}} + (u^{p^e + 1} \cdot I_0)^{1/p^{[2e]}} }
\]
etc.
%
%\pedro{I am not sure what this last sentence is saying}
%

@@

Recall that  $\Hom_R( R^{1/p^e}, R)$  is a principal $R^{1/p^e}$-module generated
the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as in \autoref{ss: math behind}, (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
%If $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$, with $1\in B$, then
%$R^{1/p^e}$ is a free $R$-module with basis
%$$\left\{ b\,  x_1^{\alpha_1/p^e} \cdots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e, b\in B \right\} ;$$
%the trace map $T$ is the projection onto the free summand
%$R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.
%
%\pedro{This paragraph is a bit redundant; we could just refer to Section~\ref{ss: math behind}}
%
